The core transcriptome of mammalian placentas and the divergence of expression with placental shape

### 2017-03-08 manuscript/manuscript.Rnw
indicate when the pubmed literature search was run

\begin{table}[tbh]
  \footnotesize
<<human.lineage.specific,echo=FALSE,results="asis">>=
hum.all.lin.spec <-
    placenta.lineage.specific.table("hum.all",
                                    lineage.table=human.mouse.lineage.specific.analysis,
                                    members=40,
                                    orderbyfc=TRUE,
                                    fdr.cutoff=0.001
                                    )
setkey(hum.all.lin.spec,"Human Symbol")
@ 
\caption{\lineagetableexplanationtypeiiishort{\human}{all other
    analyzed species} Adv. Preg. Pub. is the approximate number of
  publications indexed by PubMed mentioning this gene and an adverse
  pregnancy outcome (pre-eclampsia, premature labor, gestational
  diabetes, intrauterine growth restriction, or premature birth) and
  links to the most current PubMed search results.}
\label{tab:human_lineage_specific}
\end{table}

>>>>

\begin{table}[tbh]
  \footnotesize
<<human.lineage.specific,echo=FALSE,results="asis">>=
hum.all.lin.spec <-
    placenta.lineage.specific.table("hum.all",
                                    lineage.table=human.mouse.lineage.specific.analysis,
                                    members=40,
                                    orderbyfc=TRUE,
                                    fdr.cutoff=0.001
                                    )
setkey(hum.all.lin.spec,"Human Symbol")
@ 
\caption{\lineagetableexplanationtypeiiishort{\human}{all other
    analyzed species} The human symbol links to a brief explanation of
  the gene function in Ensembl. Adv. Preg. Pub. is the approximate
  number of publications indexed by PubMed mentioning this gene and an
  adverse pregnancy outcome (pre-eclampsia, premature labor,
  gestational diabetes, intrauterine growth restriction, or premature
  birth) as of February 2017, and links to the most current PubMed
  search results.}
\label{tab:human_lineage_specific}
\end{table}
